---
title: "Processing Urban Estates Returns"
author: "Dave Lovell"
date: "14/04/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, message = FALSE, warning = FALSE}
library("here")
library("readr")
library("dplyr")
library("digest")
library("magrittr")
library("stringr")
```
## Intro

For the time being, we're just creating a csv that makes sense and is nice to look at - so no factors or anything.

## Look see what we have here

### Read in that Data!

```{r readData, message = FALSE}
responses <- readr::read_csv(here::here("data/urbanContextData.csv"))
spec(responses)
```

## Create Unique IDs

Use hashed phone numbers, emails and postcodes. But first check that they are unique.

```{r checkphoneNumsUnique}
responses %$%
  paste0(pers_phone,pers_email,pers_postcode) -> digestThis

if(!(length(digestThis) == length(unique(digestThis))))
  error("Unique IDs are not unique!") else responses %<>% mutate(uniqueId = digest::sha1(digestThis))

#Bring uniqueId to the front
responses %<>% relocate(uniqueId)
```

### Squish all strings

(Remove double and trailing whitespace from character columns)

```{r stringSquish}
responses %<>%
  mutate(across(is.character,str_squish))
```

### Capitalise names

```{r namecapitalisation}
responses %<>% mutate(pers_name = str_to_title(pers_name))
```

### Check emails

Do they have an '@' sign ect.?

```{r checkEmails, collapse = TRUE}
  # Do any email addresses contain whitespace?
  any(str_detect(responses$pers_email, "[:space:]"), na.rm = TRUE)
  # Do all emails look a least vaguely like an email?
  all(str_detect(responses$pers_email, ".+@.+\\..+"), na.rm = TRUE)
```

### Check Phone Numbers

```{r checkPhones, collapse = TRUE}

```



